Weak Lensing Shear Inference:A Hierarchical Bayesian Approach

### 2013-03-12 docs/formula.tex
formulas

\usepackage{babel}
\begin{document}
Likelihood:

p($\epsilon_{\ell}|\vec{g},\alpha)=P(\epsilon_{0}(\epsilon_{\ell},\vec{g})|\alpha)*|\frac{\epsilon_{0}(\epsilon_{\ell},\vec{g})}{\epsilon_{\ell}}|$

Prior:

Prior($\vec{g})=1$ $|\vec{g}|<1$ else Prior(g)=0

Prior($\alpha)=exp(-\underset{i}{\xi\sum}(\alpha_{i}-\alpha_{i-1})^{2})$

Marginalized likelihood:

p($\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)p(\alpha|\vec{g})d\alpha$

with $p(\alpha|\vec{g})=Prior(\alpha)$

$p(\epsilon_{l}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)*Prior(\alpha)d\alpha$

$p(\epsilon_{\ell}|g_{1})=\underset{|g|<1}{\int}p(\epsilon_{\ell}|\vec{g})dg_{2}$
\end{document}

>>>>

\usepackage{babel}
\begin{document}
If we know the ellipticity distribution of unlensed galaxies based
on some parasmeters $\alpha$,the likelihood of reduced shear $g$
and parameter $\alpha$ is like:

\begin{equation}
L(\vec{g},\alpha|\epsilon_{\ell})=p(\epsilon_{\ell}|\vec{g},\alpha)=P(\epsilon_{0}(\vec{g})|\alpha)*|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|
\end{equation}

Note that both $\epsilon_{0}$ and $\epsilon_{\ell}$are complex numbers.So
$|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|$ is the Jacobian
determinant term.Here the prior distribtuion we use for $\vec{g}$
is a 2Dflat distribution in the region $|g|<1$.Therefore $prior(\vec{g)}=\begin{cases}
1 & |\vec{g}|<1\\
0 & |\vec{g}|>1
\end{cases}$

The prior of $\alpha$ some how depends on the model we choose for
intrinsic ellipticity distribution .When we use the step function
model for P($\epsilon_{0}$),we find that we need to use a prior on
$\alpha$ .
\begin{equation}
Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
\end{equation}

Given the likehood functions and priors we can also calculated the
marginalized likelihood function.
\begin{equation}
p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)p(\alpha|\vec{g})d\alpha
\end{equation}

Since $p(\alpha)$ does not explicitly depends on $\vec{g}$ .$p(\alpha|\vec{g})$is
just $Prior(\vec{\alpha}|\xi)$.Therefore,we have marginalized likehood
\begin{equation}
p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)Prior(\vec{\alpha}|\xi)d\alpha
\end{equation}

\end{document}
